## Evolutionary History of Siphonophore Biology

### 2017-02-14 character_coding/CharacterEvolution.Rmd
fixed spelling of monoecious/dioecious

---
title: "## Evolutionary History of the Main Biological Characters of Siphonophores"
author: "Alejandro Damian Serrano"
date: "2/11/2017"
output: html_document
---

@@

Siphonohores...

@@

Posterior probabilities of states (1 Dioeic)

@@

@@

@@

@@

##Continuous traits: Brownian motion reconstructions
###Number of bract types reconstruction:
```{r cont_bract_types, echo=F, message=F, warning=F}
contMap(ultratree, bracts)
```

@@

###Bathymetrics scattergram array
```{r depth_scattergram, echo=F, message=F, warning=F}
fancyTree(dpruned_tree,type="scattergram",X=cbind(depth_max, depth_min, depth_range, depth_median),control=list(spin=FALSE))
```

>>>>

---
title: "## Evolutionary History of Siphonophore Biology"
author: "Alejandro Damian Serrano"
output: html_document
---

@@

Siphonohores have evolved a fascinating diversity of morphological features, zooid types, life history traits, and habitats. Here we explore the evolutionary history of some of these features.

@@

Posterior probabilities of states (0 Dioecious, 1 Monoecious).

@@

Posterior probabilities of states (1 Present, 0 Absent).

@@

Posterior probabilities of states (1 Present, 0 Absent).

Physalia physalis may have reduced tentilla, which would indicate there was only one loss of tentilla at the branch leading to Apolemia.

@@

Posterior probabilities of states (1 Present, 0 Absent).

It is not clear whether or not the stem group of siphonophores had a pneumatophore.

@@

##Continuous traits: Brownian motion reconstructions
###Number of bract types reconstruction:
```{r cont_bract_types, echo=F, message=F, warning=F}
contMap(ultratree, bracts)
```
Trait = Number of Bract Types

@@

###Bathymetrics scattergram array
```{r depth_scattergram, echo=F, fig.height=11, fig.width=15, message=F, warning=F}
fancyTree(dpruned_tree,type="scattergram",X=cbind(depth_max, depth_min, depth_range, depth_median),control=list(spin=FALSE))
```
